### 2022-11-10 NSF2022/Description/backgroundv2.tex
cleaning up BG

\noindent
{\bf Collaborative Research:
Collaborative research: Self-organization modeled by moving domain
elliptic PDEs} \\
{\em Rolf Ryham (PI, Fordham University),
Bryan Quaife (lead PI, Florida State University), and
Yuan-Nan Young (PI, New Jersey Institute of Technology)}

@@

The above form a semi-linear elliptic 
system for evolution of the granules.  Equations~\eqref{eqn:stokes} are the
Stokes equations that describes the velocity $\uu$ and pressure $p$ of
the aqueous region with viscosity $\mu$.  Equation~\eqref{eqn:phase} describes the
phase transitions of the scalar order parameter $\phi$ with a decay
length $\epsilon$.
The scalar function $W(\phi)$ is a well potential where the local 
minimima representing low energy states of the water phase.
Mathematically, this order parameter is responsible for
the attraction and adhesion between granules that want to align boundaries
of like phase.

@@

The system~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
has the energy law
\begin{equation}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega_t}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{equation}
Here $E$ is the energy stored in the phase transitions.
Mathematically, the energy law states that changes
in granule configuration instantaneously change the phase energy $E$.
The dynamics are such that the change energy
is lost due to hydrodynamic dissipation.
Further details and generalizations are provided in
the Specific Aim 1 section \ref{sec:specific_aim1}.

@@

In terms of physical justification, the
derivation of the one-dimensional version of our model
was carried out by \cite{MaRa76} and \cite{ErLjCl89}
using a Landau expansion of the
free energy density for a single-well potential.
The double-well potential case was derived by
Gompper in \cite{GoHaKo94} to describe metastable coordination of water.
In the field of surface chemistry \cite{Israelachvili1954},
there is a large empirical literature on properties of
long-range hydrophobic interaction~\cite{LeRaPa77,KoNa15,
Nagle17,Lum1999, Lin2005, Meyer2006, Ducker2016,Jackson2016,Gletal88,Aketal17,Ch05}.
The stress~\eqref{eqn:stressbalance} was first
identified by PIs Ryham and Young in~\cite{Fu2018_SIAM}
and generalizes one-dimensional hydrophobic interaction to
the $n$-dimensional setting.

Finally, we mention that in the single-well case
$W(\phi) = \tfrac{1}{2}\phi^2,$ \eqref{eqn:phase} takes the form
of a screened Laplace (SL) equation $-\epsilon^2 \Delta \phi + \phi =0$.
If the material label $h_i = 1$ everywhere, then $\phi$
has a boundary layer going from $1$ at the boundary to $0$ in the bulk
and one can prove that 
\begin{equation}
\label{eqn:math_motivation}
\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS
\end{equation}
under the assumption that $\Omega$ has a class $\mathbf{C}^2$ boundary \cite{}.
In other words, the phase energy can be viewed as an
approximation of surface energy that ``extends'' into the bulk.
In the general case, $h_i^2$ replaces $1$ in \eqref{eqn:math_motivation}.
We are confident that \eqref{eq:RBT}--\eqref{eqn:stressbalance}
is a correct description of long-range surface interactions.

The model has a broad range of applicability to self-organization
phenomena in chemistry and biological physics. For one,
the formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures
exactly the right behavior expected from amphiphilic self-assembly.
For example, three bodies with amphiphilic label
(see section \ref{sec:specific_aim1}) spontaneously
self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure \ref{fig:flow_map}).
Moreover, a simple change of boundary conditions from
amphiphilic, to biased hydrophobic, to polar results in distinct
equilibrium morphologies (Figure~\ref{fig:self-assembly2}).
Since the formulation is
scale independent, it can represent a suspension of amphiphiles, where
the granules represent the mean properties of a small collection of
lipids, at the nanoscopic scale. For larger scales, the representation
is literal and the granules Janus spheres. The proposal deals with the
physical origins in section ().
\todo[inline]{
List applications; don't forget Bertozzi.}

\begin{figure}[t!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
      (a)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{long time}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)-(c) have
  the same initial configuration but different boundary conditions $g$.
  In row (a), self-assembly with an amphiphilic boundary condition
  results in a bilayer pattern shielding the hydrophobic core (yellow,
  $u > 0$) from the aqueous phase (blue, $u = 0$). Row (b) shows
  particles with a hydrophobic intensity that is greater on one side of
  the particle (magenta) than the other (yellow). In row (c), green is
  for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$. Particles
  orient like sides to form a checkerboard pattern.}
\end{figure}

\begin{figure}[t!]
\begin{center}
\includegraphics[width=\textwidth]{figures/Background/coarsening.pdf}
\end{center}
\caption{\label{fig:coarsening}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral formulation}
\label{sec:bie}

@@

\subsection{Outline of the proposal}

>>>>

\noindent
{\bf Collaborative research: Self-organization modeled by moving domain
elliptic PDEs} \\
{\em Rolf Ryham (PI, Fordham University),
Bryan Quaife (lead PI, Florida State University), and
Yuan-Nan Young (PI, New Jersey Institute of Technology)}

@@

The above form a semi-linear elliptic 
system for evolution of the granules.  Equations~\eqref{eqn:stokes} are the
Stokes equations that describes the velocity $\uu$ and pressure $p$ of
the aqueous region with viscosity $\mu$.  Equation~\eqref{eqn:phase} describes the
phase transitions of the scalar order parameter $\phi$ with a decay
length $\epsilon$.
The scalar function $W(\phi)$ is a nonnegative
well potential where the local 
minimima represent metastable states $\phi_0,$ $\phi_1$ etc. of the water phase.
To have finite bulk energy, the minimum potential phase
$\phi_0$ has $W(\phi_0) = 0.$
Mathematically, this order parameter is responsible for
the attraction and adhesion between granules that want to align boundaries
of like phase.

@@

In the absence of external flow,
the system~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
has the energy law
\begin{equation}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega_t}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{equation}
Here $E$ is the energy stored in the phase transitions.
Mathematically, the energy law states that changes
in granule configuration instantaneously change the phase energy $E$.
The dynamics are such that the change energy
is lost due to hydrodynamic dissipation.
Further details and generalizations are provided in
the Specific Aim 1 section \ref{sec:specific_aim1}.

@@

In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$
and for the background flow, we require that
$\lim_{\xx \to \infty} \uu(\xx) - \uu_{\infty}(\xx) = \mathbf{0}.$ 
In the case of shear background flow, for example,
\begin{equation}
\label{eqn:shear_BG_flow}
\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
\end{equation}
where $\dot \gamma$ is the shear rate and
$\mathbf{e}_x$, $\mathbf{e}_y$ are horizontal and vertical
basis vectors, respectively.  Other background flows include
extensional, parabolic Poiseuille, and Taylor-Green flow.
For numerical stability and physical realism,
we introduce pairwise repulsive forces and torques in \eqref{eqn:stressbalance}
to prevent the collosion between neighboring granules.
We include the repulsive potential in the energy law \eqref{eq:energy_law} 
and refer to \cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM} for details.
A background flow adds elastic energy to the granule configurations
and is quantified by simulation.

In terms of physical justification, the
derivation of the one-dimensional version of our model
was carried out by \cite{MaRa76} and \cite{ErLjCl89}
using a Landau expansion of the
free energy density for a single-well potential.
The double-well potential case was dealt with by
Gompper in \cite{GoHaKo94} to describe metastable coordination of water.
In the field of surface chemistry \cite{Israelachvili1954},
there is a large empirical literature on properties of
long-range hydrophobic interaction~\cite{LeRaPa77,KoNa15,
Nagle17,Lum1999, Lin2005, Meyer2006, Ducker2016,Jackson2016,Gletal88,Aketal17,Ch05}.
The stress~\eqref{eqn:stressbalance} was first
identified by PIs Ryham and Young in~\cite{Fu2018_SIAM}
and generalizes one-dimensional hydrophobic interaction to
the $n$-dimensional setting.

Finally, in terms of mathematical justifications, we mention
that in the single-well case
$W(\phi) = \tfrac{1}{2}\phi^2,$ \eqref{eqn:phase} takes the form
of a screened Laplace (SL) equation $-\epsilon^2 \Delta \phi + \phi =0$.
If the material label $h_i = 1$ everywhere, then $\phi$
has a boundary layer going from $1$ at the boundary to $0$ in the bulk
and one can prove that 
\begin{equation}
\label{eqn:math_motivation}
\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS
\end{equation}
under the assumption that $\Omega$ has a class $\mathbf{C}^2$ boundary \cite{}.
In other words, the phase energy can be viewed as an
approximation of surface energy that ``extends'' into the bulk.
In the general case, $h_i^2$ replaces $1$ in \eqref{eqn:math_motivation}.
We are confident that \eqref{eq:RBT}--\eqref{eqn:stressbalance}
is a correct description of long-range interactions between granule
surfaces.

\begin{wrapfigure}[23]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-5pt}
  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)-(c) have
  the same initial configuration but different boundary conditions $g$.
  In row (a), self-assembly with an amphiphilic boundary condition
  results in a bilayer pattern shielding the hydrophobic core (yellow,
  $u > 0$) from the aqueous phase (blue, $u = 0$). Row (b) shows
  particles with a hydrophobic intensity that is greater on one side of
  the particle (magenta) than the other (yellow). In row (c), green is
  for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$. Particles
  orient like sides to form a checkerboard pattern.}
\end{wrapfigure}
\subsection{Applications}
Since the formulation is scale independent,
it can be applied broad range of
nonspecific self-organization
phenomena in surface chemistry, biology and engineering.
For one,
the formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures
exactly the right behavior expected from amphiphilic self-assembly.
For example, three bodies with amphiphilic label
(see section \ref{sec:specific_aim1}) spontaneously
self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure \ref{fig:flow_map}).
Moreover, a simple change of boundary conditions from
amphiphilic, to biased hydrophobic, to polar results in distinct
equilibrium morphologies (Figure~\ref{fig:self-assembly2}).
(i)
Chemistry: Janus spheres
Since the formulation is
scale independent, it can represent a suspension of amphiphiles, where
the granules represent the mean properties of a small collection of
lipids, at the nanoscopic scale. For larger scales, the representation
is literal and the granules Janus spheres.
(ii) Pickering emulsion 
(iii) Bertozzi's problem
(iv) Tension driven microprinting
(v) Vesicle hydrodynamics.

\subsection{Vesicles as self-organized granules}
\label{sec:vesicles_as_granules}
Interface problems coming from biology are a challenging
area of applied mathematics.  Broadly speaking, these problems
involve a fluid structure interaction where the modeler must
solve for the velocity in the aqueous phase, track the interface,
and couple the velocity boundary condition to the interface through
stress balance boundary conditions.  The aqueous phase can
be a low Reynolds-number fluid, a porous medium, or viscoelastic fluid,
and the interfacial forces can come from surface tension, elasticity,
or electrostatics.
Incorporating all these details can lead to models with substantial
complexity and there is a need for robust, general models that
cut across these issues.

This section shows the principles of PDE-driven
self-organization apply to the concrete
problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
Microscopically, the membrane of a vesicle is comprised
elongated amphiphilic lipids that form inner and outer monolayers.  
The goal in vesicle hydrodynamics is to study the flow patterns e.g.,
tank-treading, tumbling, that arrise due to the interaction
between membrane elasticity and surrounding fluid.
Traditional models represent a vesicle as a
continuous surface or curve $\Sigma$.
The elastic energy takes the form
\begin{equation}
\label{eq:Canham-Helfrich}
  \int_{\Sigma} k_B(H - k_0)^2\, dS 
\end{equation}
where $H$ is the mean curvature, $k_0$ is a spontaneous curvature,
and $k_B$ is a bending modulus. 
The variation of \eqref{eq:Canham-Helfrich} gives rise to a surface force
that pointwise balances the jump in hydrodynamic stress across the interace.
A vesicle is closed surface, and so while energy does involve
the Gaussian curvature, it does not enter \eqref{eq:Canham-Helfrich}
since Gauss-Bonnet Theorem guarantees that
the integral of Gaussian curvature is independent of the shape of $\Sigma$.

Depending on the situation,
one can further enforce constant volume constraints or permeability relationships.
If the interface is area incompressible, then the surface divergence
of velocity is zero.  On the other hand, if the surface is area compressible,
then \eqref{eq:Canham-Helfrich} contains an additional stretching term of the
form $k_A(\alpha - \alpha_0)^2/\alpha_0$ where $\alpha$ and $\alpha_0$ are the
deformed and equilibrium area densitities respectively.

\begin{wrapfigure}[12]{r}{0.5\textwidth}
  \vspace{-5pt}
\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-5pt}
\caption{\label{fig:amphiphilic_assembly}
Self-organization under amphiphilic boundary condition.
(a) Granules first match hydrophobic tails (red),
(b) then align length-wise.
The principle of self-organization holds in three dimensions 
as simulated by Kohl, Corona, and Veerapaneni
\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
There are downsides to traditional models in terms of generality and physical realism.
(i) Motivated by drug delivery applications, experimenters use electric
fields, for example, to controllably open and close pores in membranes
\cite{}.
These kinds of topological changes are clumsy to incorporate into 
sharp interface formulations that assume a continuous surface \cite{}.
(ii) Sharp-interface models assume a membrane of neglible thickness. 
However, in biological processes
like fusion, fission, or insertion and penetration by proteins and peptides, 
the length scales of the
deformation (tens of nanometers) are comparable to membrane thickness (about 5 nm).
Moreover, these processes crucially rely on variable lipid
orientation relative to the surface normal (the so-called \emph{tilt}
deformation),
whereas \eqref{eq:Canham-Helfrich} implicitly assumes that the lipids
are everywhere normal to the surface.  
(iii) Finally, realistic membranes are comprised of a mixtures of lipids and proteins.
Recent work \cite{} has incorporated lipid mixtures in \eqref{eq:Canham-Helfrich},
but these models are formidably complicated 
due to the additional constraints and transport equations involved.

Diffusive interface models and surface-director models partially make up for some of
these shortcomings. 
Topological changes are permitted in phase field and level set formulations,
but these methods smear out the details of lipid orientations.
The question lipid orientations is closely related to the vast and well-studied
field of nematic liquid crystals.  Here there has been recent development
in the simulation and theory of nematic liquid crystals on surfaces.
These models consider the interplay between defects and surface geometry \cite{},
finite element formulations \cite{}, and existence of minimizers \cite{}.

\subsubsection{Main modeling innovations}
We developed the model \eqref{eq:RBT}-\eqref{eqn:hydro_stress} 
as a robust and flexible approach
that cuts across many of the aforementioned challenging aspects to vesicle modeling.
(i) The granules are not fixed to a stencil, 
affording flexibility in terms of vesicle morphology and topology--sufficiently
large forces will pull the granules apart as physically required.
(ii) The model formulation is built around important details like lipid orientations,
and exhibits and inter-monolayer slip not present in diffusive interface models.
(iii) It is straightforward to consider mixtures of granules with different
types of shapes and boundary conditions of the granules.
With the help of boundary integral equations
and fast summation methods, the dynamics can be solved in 
near-linear complexity in $N_b$, which is equal to or better than 
the computational complexity of related sharp interface methods.

Inspired
by the amphiphilic structure of lipids,
we formulated a so-called ``amphiphilic'' boundary condition
that leads a collection of granules to form bilayers.
Referring to Figure \ref{fig:amphiphilic_assembly}, 
\begin{equation}
\label{eq:amphiphilic_BC}
\phi(\mathbf{x}) = h_i(\mathbf{x}) = \tfrac{1}{2}\left(\dd_i \cdot (\xx - \aa_i)/c_i + 1\right), \quad
\mathbf{x} \in \Gamma_i,
\end{equation}
where $\dd_i$ is the director, $\aa_i$ is the center, and $c_i$ the
``radius'' of the $i$th granule.  
The phase $\phi$ takes values close to $1$ on in the direction $\dd_i$,
representing a hydrophobic tail, and values close to $0$ 
in the direction $\dd_i$ representing the hydrophilic head.

\begin{figure}[t!]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/Background/coarsening.pdf}
\end{center}
\vspace{-20pt}
\caption{\label{fig:coarsening}
Modeling procedure.
We initilize a suspension of granules.
Under the moving domain problem
\eqref{eq:RBT}-\eqref{eqn:hydro_stress}
with amphiphilic boundary condition, the granules
self-organize into vesicle bilayers.
We then introduce external hydrodynamic effects to study elastic properties.
}
\vspace{5pt}
\end{figure}
\subsubsection{How do granule-based vesicles have an elastic energy?}
A natural question to ask is how 
elastic energy enters a formulation
coming from surface interactions like \eqref{eqn:math_motivation}.
Conceptually, random suspensions of amphiphilic
granules undergo a rapid coarsening to form bilayers.
For small granule numbers, the bilayers form a single stable, ring-shaped vesicle
with energy $E_{\text{stable}}$ (Figure \ref{fig:coarsening}, (c)).
This vesicle configuration, however, is only a local minimizer,
whereas the planar configuration (Figure \ref{fig:coarsening}, (e))
is the global minimizer.  The difference between
$E(t)$ and $E_{\min}$ is the elastic energy stored by granules.
Indeed, if a background flow overcomes the energy barrier to force granules apart,
then bilayer unfolds from its circular shape into a flat shape.

When many granules are involved, the granules reach an intermediate
state consisting of several bilayer segments (see Figure \ref{fig:self-assembly2}, top right).
Placing this metastable state into a mild background flow
causes the segments to join up into isolated vesicles \cite{fu-ryh-qua-you2022}.

and we analyze its energy as follows:
\begin{enumerate}
\item[Bending]
  The vesicle has bending energy because the directors are not
  parallel.  In the outer layer, the directors have negative
  splay $\nabla \cdot \dd < 0$ and in the inner layer
  the directors have positive splay $\nabla \cdot \dd > 0$.
  Due to minimality, the energy depends locally quadratically
  on the splay and has a bending modulus $k_B$.
  When $\dd$ is everywhere parallel to the unit normal $\NN,$ then
  \[
  \nabla \dd = -2H
  \]
  where $H$ is the mean curvature. 
\item[Stretch]
  If the vesicle is stretched, then the distance between
  neighboring granules is increased from rest.  The energy
  for this increase is Hookean and for small deformations
  equals
  \begin{equation}
    \label{eq:stretch}
    \tfrac{1}{2}k_A(L - L_0)^2/L_0
  \end{equation}
  where $k_A$ is a stretching modulus, $L$ and $L_0$ are stretched
  vesicle length and length at rest, respectively
  ($\tfrac{1}{2}k_A(A - A_0)^2/A_0$ in three dimensions).
  If the stretching is too great, the vesicle ruptures
  and the free eneds either rejoin, repairing the vesicle,
  of move apart forming a flat bilayer.
\item[Tilt]
  The directors in Figure \ref{} are normal to the vesicle surface.
  However, there are situations where the directors are not normal
  to the surface and this introduces the tilt angle $\theta$
  given by $\cos \theta = \dd \cdot \NN$.
  The energy for tilt is also Hooken and behaves like
  $k_{\theta}|\dd \times \NN|^2$ for the tilt modulus $k_{\theta}$.
\end{enumerate}

\begin{wrapfigure}[11]{r}{0.5\textwidth}
\includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\caption{\label{fig:JPv_linearshear}The JP vesicles undergo tank-treading in background shear flow.}
\end{wrapfigure}

\begin{wrapfigure}[14]{l}{0.475\textwidth}
%\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture}The JP vesicles rupture under large shear rates.}
\end{wrapfigure}

This is our first step to showing the energy of the granule-based
vesicles have the same elastic energy as bilayers in the limit $N_b \to \infty$.
Once we have simulations for large systems sizes, we can provide
evidence that the two formulations are the same.
So and so has made simulations with thousands of granules in three-D
and this is now a technical/not theoretical limitation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral formulation}
\label{sec:bie}

@@

\subsection{Outline of the proposal}
The outline of the proposal goes as follows.
Section \ref{sec:resume} describes the
PIs's expertise and prior works
in (1) membrane-fluid mechanics (2) boundary integral equations
and (3) complex fluid dynamics
that are critical to the success of this proposal. 
Section \ref{sec:proposed-work}
goes over the three specific aims of the proposal.
